%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DSKE - One Page Two Column Resume
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{dske-resume-openfont}

% Essential packages - cleaned up version
\usepackage{fontawesome}  % Used for contact icons

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     THEME CONFIGURATION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Add the decoration
\namesectionFullWidth{Denis}{Škerk}{}
\pageborder

%\namesectionColumn{Denis}{Škerk}{}
%\columnbackground

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COMMON CONFIGURATION
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated{}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.31\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\sectionwithlines{Education} 
{\fontsize{\the\leftColumnFont}{\the\leftColumnLineSpace}\selectfont
{\fontsize{\the\leftSubsectionSize}{\the\leftSubsectionLineSpace}\selectfont\subsection{Strathclyde University}}
\leftdescript{MSc in Electronic \& Electrical Engineering}
{\fontsize{\the\leftColumnFont}{\the\leftColumnLineSpace}\selectfont
\location{Sep 2020 | Glasgow, Scotland \\ with distinction}}
\vspace{\leftSmallGap}

{\fontsize{\the\leftSubsectionSize}{\the\leftSubsectionLineSpace}\selectfont\subsection{\texorpdfstring{Universit\`{a} degli\\ Studi di Trieste}{Universita degli Studi di Trieste}}}
\leftdescript{BSc in Electronic Engineering}
{\fontsize{\the\leftColumnFont}{\the\leftColumnLineSpace}\selectfont
\location{Mar 2019 | Trst, Italy}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CONTACTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\sectionwithlines{Contacts}
{\fontsize{\the\leftContactFontSize}{\the\leftContactLineSpace}\selectfont
{\color{iconcolor}\faPhone}\hspace{\leftContactIconSpace} \href{tel:+393317298280}{+39 3317298280} \\[0.3em]
{\color{iconcolor}\faEnvelope}\hspace{\leftContactIconSpace} \href{mailto:skerkd@gmail.com}{skerkd@gmail.com} \\[0.3em]
{\color{iconcolor}\faLinkedin}\hspace{\leftContactIconSpace} \href{https://www.linkedin.com/in/denis-\%C5\%A1kerk/}{denisškerk} \\[0.3em]
{\color{iconcolor}\faGithub}\hspace{\leftContactIconSpace} \href{https://github.com/gib4}{gib4}}

\vspace{\leftSectionPadding}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\sectionwithlines{Coursework}
{\fontsize{\the\leftColumnFont}{\the\leftColumnLineSpace}\selectfont
{\fontsize{\the\leftSubsectionSize}{\the\leftSubsectionLineSpace}\selectfont\subsection{Graduate}}
Advanced Micro Controllers \textbullet{} 
Image \& Video Processing \textbullet{}
Advanced DSP \textbullet{} 
DSP Principles \textbullet{} 
Embedded System Design
\vspace{\leftSmallGap}

{\fontsize{\the\leftSubsectionSize}{\the\leftSubsectionLineSpace}\selectfont\subsection{Undergraduate}}
Electronics \textbullet{} 
Telecommunications \textbullet{} 
Computer Networks \textbullet{} 
Automation \textbullet{}
Economics
}

\vspace{\leftSectionPadding}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\sectionwithlines{Skills}
{\fontsize{\the\leftColumnFont}{\the\leftColumnLineSpace}\selectfont
{\fontsize{\the\leftSubsectionSize}{\the\leftSubsectionLineSpace}\selectfont\subsection{Programming}}
Dart \textbullet{} Python \textbullet{} Perl \textbullet{} C \textbullet{} C++ \textbullet{} QT Designer
\vspace{\leftSmallGap}

{\fontsize{\the\leftSubsectionSize}{\the\leftSubsectionLineSpace}\selectfont\subsection{OS \& other}}
Flutter \textbullet{} Linux Red Hat \textbullet{} \LaTeX{} \textbullet{} HTML
\vspace{\leftSmallGap}

{\fontsize{\the\leftSubsectionSize}{\the\leftSubsectionLineSpace}\selectfont\subsection{Languages}}
English {\footnotesize(native)} \textbullet{} Slovenian {\footnotesize(native)} \textbullet{} Italian {\footnotesize(native)}
\vspace{\leftSmallGap}

{\fontsize{\the\leftSubsectionSize}{\the\leftSubsectionLineSpace}\selectfont\subsection{Interpersonal Skills}}
Adaptable \textbullet{} Conflict resolution \textbullet{} Active listener
}
\vspace{\leftSectionPadding}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  

\sectionwithlines{Interests}
{\fontsize{\the\rightColumnFont}{\the\rightColumnLineSpace}\selectfont
Music composition \textbullet{} Consumer Tech \textbullet{} Tennis
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hspace{\rightColumnSpace}
\begin{minipage}[t]{0.62\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\sectionwithlines{Career Experience}
\runsubsection{u-blox}
\rightdescript{| Specialist Engineer {-} Validation Modules IoT}
\location{Apr 2024 – Present | Sgonico, Italy}
\vspace{\topsep}
\begin{tightemize}
\item \textbf{Network Services Testing}: Developed and executed tests for network services in Perl, focusing on cellular modules' functionality.
\item \textbf{PSM Testing}: Developed and executed tests in Perl to validate cellular modules' Power Saving Mode functionality and power consumption optimization.
\item \textbf{Automation Development}: Contributed to automating a Linux-based network simulator within the Automated Testing environment using Python and Perl.
\item \textbf{GUI Development}: Created a graphical interface using custom Tkinter library in Python for module piloting, integrating with existing terminal control for cost reduction.
\end{tightemize}
\sectionsep{}

\runsubsection{Leonardo {-} Electronics}
\rightdescript{| Avionic Software Engineer {-} Ext. Consultant}
\location{May 2021 – Mar 2024 | Ronchi dei Legionari, Italy}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item \textbf{Radar Simulation}: Developed C++ models and simulations for radar systems in a multi-process environment utilizing shared memory communication.
\item \textbf{UI Development}: Created radar testing interface using QT Designer 5 to streamline testing procedures.
\item \textbf{Systems Engineering}: Led system requirements definition and modeling efforts for radar systems.
\item \textbf{Documentation}: Authored technical documentation adhering to MIL-STD specifications and guidelines.
\end{tightemize}

\sectionsep{}

\runsubsection{RB}
\rightdescript{| Photovoltaic System Designer}
\location{Nov 2020 – April 2021 | Frazione Stazione Prosecco, Italy}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item \textbf{Process Automation}: Led initiatives to streamline and automate workflows for photovoltaic system design.
\item \textbf{System Design}: Developed design solutions and pricing strategies for photovoltaic systems with storage.
\end{tightemize}

\sectionsep{}
\runsubsection{Mipot Hi-Tech Company S.p.A.}
\rightdescript{| Software Engineering Intern in R\&D Department }
\location{Nov 2017, Oct 2018 {-} Mar 2019| Cormons, Italy}
\vspace{\topsep}
\begin{tightemize}
\item \textbf{Protocol Development}: Engineered a protocol bridge between Modbus (RS-485) devices and LoRaWAN RTX module utilizing microcontroller and UART communication.
\item \textbf{Hardware Integration}: Designed and implemented adaptation circuits for seamless interface between Modbus devices and microcontrollers.
\item \textbf{Power Consumption Optimization}: Analyzed and optimized RF receiving unit performance to achieve 100\% receiving rate while minimizing power consumption, conducting energy efficiency validation within HCS protocol constraints.
\end{tightemize}

\sectionsep{}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\sectionwithlines{Projects}
\runsubsection{ECG generation using GAN}
\rightdescript{| MSc Dissertation}
\location{May 2020 – Aug 2020 | Glasgow, Scotland}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Use a Generative Adversarial Network on Pythorch framework to generate the electrocardiograms.
\item Pre-process the MIT-BIH arrhythmia dataset on Matlab.
\item Model tested on Google's platform Colab.
\end{tightemize}

\end{minipage} 
\end{document}
